pema application

### 2022-12-05 paper/manuscript.Rmd
update 2022-12-02 06:43:24
changed "regularizing horseshoe" to "regularized horseshoe" throughout

<span id = "openingparagraph">A common application of meta-analysis is to summarize existing bodies of literature.
A crucial challenge is that there is often substantial heterogeneity between studies,
because similar research questions are studied in different labs,
sampling from different populations,
and using different study designs, instruments, and methods.
Any of those between-studies differences can introduce *systematic heterogeneity* in observed effect sizes.
Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
or controlled for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
The latter approach provides an opportunity to learn which factors impact the effect size
found.
However, a limitation of meta-regression is that it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
In applied meta-analyses, the number of available studies is often low [@rileyInterpretationRandomEffects2011].
This introduces a risk of overfitting,
which results in uninterpretable model parameters [@hastieElementsStatisticalLearning2009].
In extreme cases, the ratio of cases to parameters can be so low that the model is not (empirically) identified,
resulting in non-convergence [@akaikeNewLookStatistical1974].
Accounting for between-studies heterogeneity thus poses a non-trivial challenge to classic meta-analytic methods.
The risk of arriving at false-positive conclusions
when there are many potential moderators is so ubiquitous that it was referred to as the "primary pitfall" in meta-regression [@thompsonHowShouldMetaregression2002].
The present study introduces a novel method to overcome this pitfall by imposing Bayesian regularizing (LASSO and regularizing horseshoe) priors on the regression coefficients.
These priors shrink the effect of irrelevant predictors towards zero while leaving important predictors relatively unaffected.
The result is a sparse model with fewer non-zero parameters,
which benefits model convergence, reduces overfitting, and helps identify relevant between-study differences.
</span>

@@

An alternative solution is data-driven variable selection using appropriate statistical techniques.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning for variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This prior work used the non-parametric *random forest* algorithm.
A limitation of random forests is that its results are harder to interpret than linear models,
which describe the effect of each moderator with a single parameter.
The present study instead uses *regularization*,
which is a method for variable selection in linear models.
Regularization shrinks small model parameters towards zero,
such that irrelevant moderators are eliminated.
Different approaches to regularization exist [@hastieElementsStatisticalLearning2009].
<span id = "lassointroduction">The present paper introduces *Bayesian Regularized Meta-Regression* (BRMA),
an algorithm that uses Bayesian regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability density to near-zero values,
which shrinks small regression coefficients towards zero, thus resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and regularizing horseshoe prior.</span>

@@

<span id = "reftibshirani">To understand how regularized regression introduces bias, consider a comparison between ordinary least squares regression and LASSO regression [for a more elaborate introduction, see @tibshiraniRegressionShrinkageSelection2011].</span>
Ordinary least squares regression (OLS) estimates model parameters by minimizing the Residual Sum of Squares (RSS) of the outcome variable, given by the formula below.
In this equation, $n$ is the number of participants; $y_i$ is the outcome variable, and $x$ is one of $p$ predictor variables.
\begin{align}
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
\end{align}
The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data.
Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
Most common is the LASSO penalty, which consists of the sum of the absolute regression coefficients, or the L1 norm [@hastieElementsStatisticalLearning2009].
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
The amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
As $\lambda$ increases,
all coefficients shrink towards zero, ultimately producing the null model.
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
The LASSO penalized residual sum of squares is given by:
\begin{align}
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
\end{align}
<span id = "whylasso">Note that many other regularizing penalties exist.
This introduction focuses on the LASSO penalty because it is most ubiquitous, easy to understand,
and has an analogue in Bayesian estimation,
as explained in the next section.</span>

@@

<span id = "horseshoe">One limitation of the LASSO prior is that it biases all regression coefficients towards zero - for relevant as well as irrelevant moderators.
To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
These priors still pull small regression coefficients towards zero,
but exert less bias on larger regression coefficients.
One example is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.
One limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
The regularizing horseshoe was introduced to overcome this limitation [@PiironenVehtari2017b].</span></span>

The BRMA method introduced here offers both LASSO and regularizing horseshoe priors.
The LASSO prior is given by:
\begin{align}
\beta_{j} &\sim \text{DE}(0, \frac{s}{\lambda})\\ (\#eq:lasso)
\lambda &\sim \chi^2(0, \nu_1)
\end{align}
where DE denotes the double exponential distribution centered around zero,
with a scale determined by a global scale parameter $s$ that is multiplied by the inverse of tuning parameter $\lambda$.
Increasing the scale parameter extends the prior to cover more extreme values.
The inverse tuning parameter is estimated from the data 
by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$ [@vanErpOberskiMulder2019].
Increasing the degrees of freedom assigns greater probability mass to extreme values, resulting in less regularization.
The present study used default values for the prior parameters,
$s = 1$, $\nu_1 = 1$, as suggested by @vanErpOberskiMulder2019.

The regularizing horseshoe prior combines global and local shrinkage of the regression coefficients with a finite slab that curtails the occurrence of very extreme values [@PiironenVehtari2017b].
For regression coefficients $\beta_j$, for $j \in [1\ldots p]$ where $p$ is the total number of moderators,
the regularizing horseshoe prior is given by:
\begin{align}
\beta_{j} &\sim N(0, \tilde{\tau}_j^2\lambda) \text{, with}\\ (\#eq:hs)
\tilde{\tau}_j^2 &= \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2}\\
\lambda &\sim \text{student-}t^+(\nu_1, 0, \lambda^2_0)\\
\tau_j &\sim \text{student-}t^+(\nu_2, 0, 1)\\
c^2 &\sim \Gamma^{-1}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
\end{align}
Note that global shrinkage parameters, which are not subscripted, affect all regression coefficients.
Local parameters are indicated by subscript $_j$, and affect each individual regression coefficient separately.
In these equations, $N$ denotes the normal distribution,
student-$t^+$ denotes the positive half of a t distribution,
and $\Gamma^{-1}$ denotes the inverse Gamma distribution. 
In this formula, $\lambda$ controls the overall scale of the priors for all regression coefficients,
where larger values for the global scale parameter $\lambda^2_0$ widen the rande of values covered by the priors.
The global degrees of freedom $\nu_1$ control the overall thickness of the tails,
with higher values resulting in thinner tails, which assigning less probability mass to extreme values.
Lighter tails can aid model convergence when the model is weakly identified; for example, when there are more moderators than observations.
The prior $\tau_j$ controls the local shrinkage of specific regression coefficients;
its scale is fixed, but its degrees of freedom $\nu_2$ control the incidence of extreme values in a similar way as $\nu_1$.
A finite "slab" applies additional regularization to very large coefficients,
which provides greater numerical stability of the model.
This slab is governed by a degrees of freedom parameter $\nu_3$ and a scale parameter $s$.
As before, increasing $\nu_3$ assigns less probability mass to extreme values.
Increasing $s$ increases the range of values covered by the slab.

@@

As explained earlier,
regularization penalizes all coefficients equally,
without regard for their scale.
If variables are on different scales,
this can lead to uneven penalization of coefficients in which
variables with smaller standard deviations are biased more strongly towards zero [@lee2015note].
If the scale of predictor $x$ is increased by a factor 10,
its regression coefficient is reduced by a factor 10,
bringing it closer to zero where it will be more affected by penalization.
Standardization is a widely used method for equalizing predictor scales [@gelmanScalingRegressionInputs2008a].
Standardization is a linear transformation that sets the mean of all predictors to 0 and their standard deviation to 1.
Like most other regularizing methods,
BRMA performs standardization by default [@tibshirani1996].
After parameters are estimated using standardized variables,
they can be restored to their original scales.
For the intercept, the transformation is:
$$
b_0 = b_{0Z} - \mathbf{b}_Z\frac{\bar{\mathbf{x}}}{\mathbf{s}_X}
$$
where $b_0$ is the intercept, $b_{0Z}$ is the intercept for the standardized predictors,
$\mathbf{\bar{x}}$ and $\mathbf{s}_{x}$ are the vectors of predictor means and variances,
and $\mathbf{b_Z}$ is the vector of regression coefficients for the standardized predictors.
The regression coefficients are returned to their original scale by applying:
$$
\mathbf{b}_x = \frac{\mathbf{b}_z}{\mathbf{s}_x}
$$

@@

As mentioned before, the R-implementation of BRMA has several options that can be customized.
The most important option relates to the choice of priors for the regression coefficients.
At the time of writing, `brma()` supports two priors for regression coefficients: the LASSO and the regularizing horseshoe.
A prior is selected using the `method` argument;
the `prior` argument is used to specify custom values for the prior hyperparameters (see Statistical underpinnings).
The parameters of the LASSO prior are explained in Equation \@ref(eq:lasso),
and those of the regularizing horseshoe in Equation \@ref(eq:hs).
Table \@ref(tab:tabprior) provides an overview of the arguments that can be passed to `prior` to control these parameters,
along with a rudimentary description of the effect of increasing the value of each parameter.
<!-- The default values in this table correspond to the values used for the present simulation study, and are based on prior research [@vanErpOberskiMulder2019; @PiironenVehtari2017a]. -->

@@

We performed a simulation study to validate the BRMA algorithm.
As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation [RMA, @viechtbauerConductingMetaanalysesMetafor2010],
which is the current state-of-the-art in the field.
We evaluated the algorithms' predictive performance in new data, 
ability to perform variable selection,
and ability to recover population parameters.
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
and which prior (LASSO versus regularizing horseshoe) is to be preferred.
<span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
Default values for the LASSO prior were based on @vanErpOberskiMulder2019,
and default values for the regularizing horseshoe prior were based on @PiironenVehtari2017a.</span>
All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.

@@

First, we estimate a model with all default settings.
Based on the results of the present simulation study, the regularizing horseshoe is the default prior.
To see all default values, open the function documentation using `?brma`.
The use of a random seed makes this example reproducible:
```{r exmodel1, echo = TRUE, eval = FALSE}
fit <- brma(yi ~ ., data = df, vi = "vi", seed = 1)
```
```{r, echo = FALSE, eval = run_everything}
fit <- brma(yi ~ ., data = df, vi = "vi", seed = 1)
saveRDS(fit, "fit.RData")
```
```{r, echo = FALSE, eval = TRUE}
fit <- readRDS("fit.RData")
```
Running `summary(fit)` returns the posterior mean, standard deviation, and quantiles of the model parameters (see Table \@ref(tab:tabsumex)).
Use the posterior mean or median (50% quantile) and 95% credible interval (2.5% - 97.5%) to perform inference on model parameters.
<!-- In the simulation study, -->
<!-- we retained moderators when the 95% credible interval excluded zero, -->
<!-- Since Bayesian penalization does not automatically shrink estimates exactly to zero. -->
Parameters whose 95% credible interval excludes zero are marked with an asterisk.
Note that Bayesian analyses do not use the frequentist notion of significance.
Instead, we say that there is a 95% probability that the true population parameter lies within the interval,
given the prior and observed data.
In this example, there are no moderators for which the 95\% CI excludes zero.
The residual heterogeneity, however, does exceed zero.
The `brma()` function builds upon the `rstan` package,
and its output is backwards compatible.
A `brma` model can be converted to a `stanfit` object via `as.stan(fit)`.
This makes it possible to benefit from the many existing convenience functions for `rstan` models.
For example, it is possible to get a HPDI interval for the residual heterogeneity by running `bayestestR::hdi(as.stan(fit), parameters = "tau2")`.
There are also many plotting functions for `stanfit` objects;
for example, one can plot the model parameters using `plot(as.stan(fit), plotfun = "dens", pars = c("Intercept", "year"))`.

@@

This study presented a novel algorithm to select relevant moderators that can explain heterogeneity in meta-analyses, using Bayesian shrinkage priors. 
A simulation study validated the performance of two versions of the BRMA algorithm, with a regularizing horseshoe prior and LASSO prior, relative to state-of-the-art meta-regression with restricted maximum likelihood estimation (RMA).
Our analyses examined the algorithms' predictive performance, which is a measure of generalizability,
their ability to perform variable selection,
and ability to recover population parameters.
Our research questions were whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
and which prior (horseshoe versus LASSO) is to be preferred.

>>>>

<span id = "openingparagraph">A common application of meta-analysis is to summarize existing bodies of literature.
A crucial challenge is that there is often substantial heterogeneity between studies,
because similar research questions are studied in different labs,
sampling from different populations,
and using different study designs, instruments, and methods.
Any of those between-studies differences can introduce *systematic heterogeneity* in observed effect sizes.
Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
or controlled for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
The latter approach provides an opportunity to learn which factors impact the effect size
found.
However, a limitation of meta-regression is that it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
In applied meta-analyses, the number of available studies is often low [@rileyInterpretationRandomEffects2011].
This introduces a risk of overfitting,
which results in uninterpretable model parameters [@hastieElementsStatisticalLearning2009].
In extreme cases, the ratio of cases to parameters can be so low that the model is not (empirically) identified,
resulting in non-convergence [@akaikeNewLookStatistical1974].
Accounting for between-studies heterogeneity thus poses a non-trivial challenge to classic meta-analytic methods.
The risk of arriving at false-positive conclusions
when there are many potential moderators is so ubiquitous that it was referred to as the "primary pitfall" in meta-regression [@thompsonHowShouldMetaregression2002].
The present study introduces a novel method to overcome this pitfall by imposing Bayesian regularizing (LASSO and regularized horseshoe) priors on the regression coefficients.
These priors shrink the effect of irrelevant predictors towards zero while leaving important predictors relatively unaffected.
The result is a sparse model with fewer non-zero parameters,
which benefits model convergence, reduces overfitting, and helps identify relevant between-study differences.
</span>

@@

An alternative solution is data-driven variable selection using appropriate statistical techniques.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning for variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This prior work used the non-parametric *random forest* algorithm.
A limitation of random forests is that its results are harder to interpret than linear models,
which describe the effect of each moderator with a single parameter.
The present study instead uses *regularization*,
which is a method for variable selection in linear models.
Regularization shrinks small model parameters towards zero,
such that irrelevant moderators are eliminated.
Different approaches to regularization exist [@hastieElementsStatisticalLearning2009].
<span id = "lassointroduction">The present paper introduces *Bayesian Regularized Meta-Regression* (BRMA),
an algorithm that uses Bayesian regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability density to near-zero values,
which shrinks small regression coefficients towards zero, thus resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and regularized horseshoe prior.</span>

@@

<span id = "reftibshirani">To understand how regularized regression introduces bias, consider a comparison between ordinary least squares regression and LASSO regression [for a more elaborate introduction, see @tibshiraniRegressionShrinkageSelection2011].</span>
Ordinary least squares regression (OLS) estimates model parameters by minimizing the Residual Sum of Squares (RSS) of the outcome variable, given by the formula below.
In this equation, $n$ is the number of participants; $y_i$ is the outcome variable, and $x$ is one of $p$ predictor variables.
\begin{align}
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
\end{align}
The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data.
Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
Most common is the LASSO penalty, which consists of the sum of the absolute regression coefficients, or the L1 norm [@hastieElementsStatisticalLearning2009].
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
The amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
As $\lambda$ increases,
all coefficients shrink towards zero, ultimately producing the null model.
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
The LASSO penalized residual sum of squares is given by:
\begin{align}
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}| (\#eq:prss)
\end{align}
<span id = "whylasso">Note that many other regularizing penalties exist.
This introduction focuses on the LASSO penalty because it is most ubiquitous, easy to understand,
and has an analogue in Bayesian estimation,
as explained in the next section.</span>

@@

<span id = "horseshoe">One limitation of the LASSO prior is that it biases all regression coefficients towards zero - for relevant as well as irrelevant moderators.
To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
These priors still pull small regression coefficients towards zero,
but exert less bias on larger regression coefficients.
One example is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.
One limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
The regularized horseshoe was introduced to overcome this limitation [@PiironenVehtari2017b].</span></span>

The BRMA method introduced here offers both LASSO and regularized horseshoe priors.
The LASSO prior is given by:
\begin{align}
\beta_{j} &\sim \text{DE}(0, \frac{s}{\lambda})\\ (\#eq:lasso)
\lambda &\sim \chi^2(0, \nu_1)
\end{align}
where DE denotes the double exponential distribution centered around zero,
with a scale determined by a global scale parameter $s$ that is multiplied by the inverse of tuning parameter $\lambda$.
Increasing the scale parameter extends the prior to cover more extreme values.
The inverse tuning parameter is estimated from the data 
by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$ [@vanErpOberskiMulder2019].
Increasing the degrees of freedom assigns greater probability mass to extreme values, resulting in less regularization.
The present study used default values for the prior parameters,
$s = 1$, $\nu_1 = 1$, as suggested by @vanErpOberskiMulder2019.

The regularized horseshoe prior combines global and local shrinkage of the regression coefficients with a finite slab that curtails the occurrence of very extreme values [@PiironenVehtari2017b].
For regression coefficients $\beta_j$, for $j \in [1\ldots p]$ where $p$ is the total number of moderators,
the regularized horseshoe prior is given by:
\begin{align}
\beta_{j} &\sim N(0, \tilde{\tau}_j^2\lambda) \text{, with}\\ (\#eq:hs)
\tilde{\tau}_j^2 &= \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2}\\
\lambda &\sim \text{student-}t^+(\nu_1, 0, \lambda^2_0)\\
\tau_j &\sim \text{student-}t^+(\nu_2, 0, 1)\\
c^2 &\sim \Gamma^{-1}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
\end{align}
Note that global shrinkage parameters, which are not subscripted, affect all regression coefficients.
Local parameters are indicated by subscript $_j$, and affect each individual regression coefficient separately.
In these equations, $N$ denotes the normal distribution,
student-$t^+$ denotes the positive half of a t distribution,
and $\Gamma^{-1}$ denotes the inverse Gamma distribution. 
In this formula, $\lambda$ controls the overall scale of the priors for all regression coefficients,
where larger values for the global scale parameter $\lambda^2_0$ widen the rande of values covered by the priors.
The global degrees of freedom $\nu_1$ control the overall thickness of the tails,
with higher values resulting in thinner tails, which assigning less probability mass to extreme values.
Lighter tails can aid model convergence when the model is weakly identified; for example, when there are more moderators than observations.
The prior $\tau_j$ controls the local shrinkage of specific regression coefficients;
its scale is fixed, but its degrees of freedom $\nu_2$ control the incidence of extreme values in a similar way as $\nu_1$.
A finite "slab" applies additional regularization to very large coefficients,
which provides greater numerical stability of the model.
This slab is governed by a degrees of freedom parameter $\nu_3$ and a scale parameter $s$.
As before, increasing $\nu_3$ assigns less probability mass to extreme values.
Increasing $s$ increases the range of values covered by the slab.

@@

As explained in Formula \@ref(eq:prss),
regularization penalizes all coefficients equally,
without regard for their scale.
If variables are on different scales,
this can lead to uneven penalization of coefficients in which
variables with smaller standard deviations are biased more strongly towards zero [@lee2015note].
If the scale of predictor $x$ is increased by a factor 10,
its regression coefficient is reduced by a factor 10,
bringing it closer to zero where it will be more affected by penalization.
Standardization is a widely used method for equalizing predictor scales [@gelmanScalingRegressionInputs2008a].
Standardization is a linear transformation that sets the mean of all predictors to 0 and their standard deviation to 1.
Like most other regularizing methods,
BRMA performs standardization by default [@tibshirani1996].
After parameters are estimated using standardized variables,
they can be restored to their original scales.
For the intercept, the transformation is:
$$
b_0 = b_{0Z} - \mathbf{b}_Z\frac{\bar{\mathbf{x}}}{\mathbf{s}_X}
$$
where $b_0$ is the intercept, $b_{0Z}$ is the intercept for the standardized predictors,
$\mathbf{\bar{x}}$ and $\mathbf{s}_{x}$ are the vectors of predictor means and variances,
and $\mathbf{b_Z}$ is the vector of regression coefficients for the standardized predictors.
The regression coefficients are returned to their original scale by applying:
$$
\mathbf{b}_x = \frac{\mathbf{b}_z}{\mathbf{s}_x}
$$

@@

As mentioned before, the R-implementation of BRMA has several options that can be customized.
The most important option relates to the choice of priors for the regression coefficients.
At the time of writing, `brma()` supports two priors for regression coefficients: the LASSO and the regularized horseshoe.
A prior is selected using the `method` argument;
the `prior` argument is used to specify custom values for the prior hyperparameters (see Statistical underpinnings).
The parameters of the LASSO prior are explained in Equation \@ref(eq:lasso),
and those of the regularized horseshoe in Equation \@ref(eq:hs).
Table \@ref(tab:tabprior) provides an overview of the arguments that can be passed to `prior` to control these parameters,
along with a rudimentary description of the effect of increasing the value of each parameter.
<!-- The default values in this table correspond to the values used for the present simulation study, and are based on prior research [@vanErpOberskiMulder2019; @PiironenVehtari2017a]. -->

@@

We performed a simulation study to validate the BRMA algorithm.
As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation [RMA, @viechtbauerConductingMetaanalysesMetafor2010],
which is the current state-of-the-art in the field.
We evaluated the algorithms' predictive performance in new data, 
ability to perform variable selection,
and ability to recover population parameters.
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
and which prior (LASSO versus regularized horseshoe) is to be preferred.
<span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
Default values for the LASSO prior were based on @vanErpOberskiMulder2019,
and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>
All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.

@@

First, we estimate a model with all default settings.
Based on the results of the present simulation study, the regularized horseshoe is the default prior.
To see all default values, open the function documentation using `?brma`.
The use of a random seed makes this example reproducible:
```{r exmodel1, echo = TRUE, eval = FALSE}
fit <- brma(yi ~ ., data = df, vi = "vi", seed = 1)
```
```{r, echo = FALSE, eval = run_everything}
fit <- brma(yi ~ ., data = df, vi = "vi", seed = 1)
saveRDS(fit, "fit.RData")
```
```{r, echo = FALSE, eval = TRUE}
fit <- readRDS("fit.RData")
```
Running `summary(fit)` returns the posterior mean, standard deviation, and quantiles of the model parameters (see Table \@ref(tab:tabsumex)).
Use the posterior mean or median (50% quantile) and 95% credible interval (2.5% - 97.5%) to perform inference on model parameters.
<!-- In the simulation study, -->
<!-- we retained moderators when the 95% credible interval excluded zero, -->
<!-- Since Bayesian penalization does not automatically shrink estimates exactly to zero. -->
Parameters whose 95% credible interval excludes zero are marked with an asterisk.
Note that Bayesian analyses do not use the frequentist notion of significance.
Instead, we say that there is a 95% probability that the true population parameter lies within the interval,
given the prior and observed data.
In this example, there are no moderators for which the 95\% CI excludes zero.
The residual heterogeneity, however, does exceed zero.
The `brma()` function builds upon the `rstan` package,
and its output is backwards compatible.
A `brma` model can be converted to a `stanfit` object via `as.stan(fit)`.
This makes it possible to benefit from the many existing convenience functions for `rstan` models.
For example, it is possible to get a HPDI interval for the residual heterogeneity by running `bayestestR::hdi(as.stan(fit), parameters = "tau2")`.
There are also many plotting functions for `stanfit` objects;
for example, one can plot the model parameters using `plot(as.stan(fit), plotfun = "dens", pars = c("Intercept", "year"))`.

@@

This study presented a novel algorithm to select relevant moderators that can explain heterogeneity in meta-analyses, using Bayesian shrinkage priors. 
A simulation study validated the performance of two versions of the BRMA algorithm, with a regularized horseshoe prior and LASSO prior, relative to state-of-the-art meta-regression with restricted maximum likelihood estimation (RMA).
Our analyses examined the algorithms' predictive performance, which is a measure of generalizability,
their ability to perform variable selection,
and ability to recover population parameters.
Our research questions were whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
and which prior (horseshoe versus LASSO) is to be preferred.
